A new method to explicitly estimate the shift of optimum along gradients in multispecies studies

### 2023-01-10 redaction/manuscript_cut.Rmd
Update figures formulation
Use latex formulation instead of Rmd formulation

```{r fig1, fig.cap="Example of the simulation process for two scenarios each broken down in three categories of sub-scenarios: (a) the sampling design either uniform (A1) or unbalanced (A2) (b) the optimum positions for the first (full points) and second (circles) sampling occasions of the 20 species, which is either in the middle (green area) or close to the edges (orange areas) of the sampling range in variable proportions depending on sub-scenario category (B1: 100\\% middle, B2: 70\\% middle) (c) the ecological specialization of species, which can be specialist (dark curves) or generalist species (purple curves) in variable proportions depending on the sub-scenario category (100\\% in C1 or 50\\% in C2 of specialist species). The bottom panel represents (d) the species response curves for the first and second sampling occasion (solid and dashed lines) of the two scenarios that results in the combination of the three sub-scenarios above.", fig.dim=c(8.3, 9.4)}

cowplot::plot_grid(g_subscenarA, g_subscenarB, g_subscenarC, g_scenar, 
                   nrow=4,
                   labels=c("(a)", "(b)","(c)","(d)"),
                   label_size = 12)
```

@@

```{r fig2, fig.dim=c(8.3, 10.4), fig.cap = "Distribution of species specific performance metrics for the eight simulated scenarios after 30 replications. The colour of the points represents species optimum position along the simulated gradient  (in the edge, orange points, or in the middle, green points). Shape of points corresponds to species ecological specialization type relative to the width of their ecological niche (generalist species with broad ecological niche, represented by inverted triangles, or specialist species with narrower ecological niche, represented by circles)."}
fig2
```

@@

```{r fig3, fig.dim=c(8.3,7), fig.cap="Shift estimates following three statistical methods on 24 Orthoptera species optimum positions between 1980–1988 and 2018–2019 along an elevational gradient in Mercantour National Park (French Alps). The points correspond to the mean estimates and the segments to the associated 95\\% credible or confidence intervals. The black horizontal lines represent graphical range, segments reaching those lines indicate intervals wider than the graphical range. Species are ordered by increasing optimum estimates of the first period. Species names are coloured depending on the optimum position types with edge species coloured in orange and middle species in green. Presence (or absence) of asterisk indicates species ecological type as defined in the simulation study (presence: generalist, absence: specialist)."}

fig3

@@

## Data availability
The data and R scripts used to produce this manuscript will be available on GitHub and archived on Zenodo before publication.

>>>>

\begin{figure}[H]

\vspace*{-0mm}
{\centering \includegraphics{../results/figs/fig1.pdf}

}
\vspace*{-1mm}
\caption{(double column) Example of the simulation process for two scenarios each broken down in three categories of sub-scenarios: (a) the sampling design either uniform (A1) or unbalanced (A2) (b) the optimum positions for the first (full points) and second (circles) sampling occasions of the 20 species, which is either in the middle (green area) or close to the edges (orange areas) of the sampling range in variable proportions depending on sub-scenario category (B1: 100\% middle, B2: 70\% middle) (c) the ecological specialization of species, which can be specialist (dark curves) or generalist species (purple curves) in variable proportions depending on the sub-scenario category (100\% in C1 or 50\% in C2 of specialist species). The bottom panel represents (d) the species response curves for the first and second sampling occasion (solid and dashed lines) of the two scenarios that results in the combination of the three sub-scenarios above.}\label{fig:fig1}
\end{figure}

@@

\begin{figure}[H]
\vspace*{-0mm}
{\centering \includegraphics{../results/figs/fig2.pdf}

}
\vspace*{-1mm}

\caption{(double column) Distribution of species specific performance metrics for the eight simulated scenarios after 30 replications. The colour of the points represents species optimum position along the simulated gradient  (in the edge, orange points, or in the middle, green points). Shape of points corresponds to species ecological specialization type relative to the width of their ecological niche (generalist species with broad ecological niche, represented by inverted triangles, or specialist species with narrower ecological niche, represented by circles).}\label{fig:fig2}
\end{figure}

@@

\begin{figure}[H]

\vspace*{-0mm}
{\centering \includegraphics{../results/figs/fig3.pdf}

}
\vspace*{-1mm}

\caption{(double column) Shift estimates following three statistical methods on 24 Orthoptera species optimum positions between 1980–1988 and 2018–2019 along an elevational gradient in Mercantour National Park (French Alps). The points correspond to the mean estimates and the segments to the associated 95\% credible or confidence intervals. The black horizontal lines represent graphical range, segments reaching those lines indicate intervals wider than the graphical range. Species are ordered by increasing optimum estimates of the first period. Species names are coloured depending on the optimum position types with edge species coloured in orange and middle species in green. Presence (or absence) of asterisk indicates species ecological type as defined in the simulation study (presence: generalist, absence: specialist).}\label{fig:fig3}
\end{figure}

@@

## Data availability
The data and R scripts used to produce this manuscript are archived on Zenodo: . The outputs of the Bayesian models used to produce the results presented in this paper are available as a Dryad's repository at: https://doi.org/10.5061/dryad.0gb5mkm59.
